Newly Left-Behind Children's Educational Performance Drops Slightly After Parental Migration

### 2023-06-09 MScThesisText.Rmd
Update code, writing, bibliography

note: |
  An earlier version of this article was submitted in partial fulfillment of the requirements for the degree -- Master of Science in Societal Resilience (Research)
authornote: |

@@

I adopted `R` (version 4.2.2) for all the analyses [@R-base]. This involved the following packages: `tidyverse` (version 2.0.0) and `haven` (version 2.5.2) for data cleaning [@R-tidyverse; @R-haven]; `fixest` (version 0.11.1) for econometric modeling [@R-fixest]; `MatchIt` (version 4.5.2) and `cobalt` (version 4.5.0) for matching [@ho2011; @R-MatchIt; @R-cobalt]; `modelsummary` (version 1.3.0), `vtable` (version 1.4.2), and `kableExtra` (version 1.3.4) for presenting the results [@R-modelsummary; @R-vtable; @R-kableExtra]; and `papaja` (version 0.1.1) for typesetting [@R-papaja].

@@

My research adds to the burgeoning evidence in favor of policy change on the hukou system. China's multilevel citizenship scheme powered by hukou shall not remain as it is, despite the small reduction of newly left-behind children's schooling performance. The slight drop is only the short-term consequence; The lifelong cumulative effect on children may be extensive [@liang2020; @meng2017]. Besides, educational attainment is only part of human development outcomes. Other outcomes like mental health and non-cognitive skills are also subjected to parental absence's influence [@antia2020; @pang2022]. Policymakers should accelerate the reforms on hukou, opening more doors for parents to migrate together with their children. In January 2023, local government officials lifted hukou restrictions in Zhengzhou, a city that hosts twelve million residents and the world's largest iPhone manufacturing plant [@jiemiannews2023; @deng2023]. This metropolis in central China set the precedant for offering hukou to all arriving migrants. Other main cities should follow suit. Besides top-down policymaking, bottom-up approaches are also necessary. School administrators could dedicate more advisory and counseling programs. Social workers could provide paraprofessional training in communities [@wang2020a].

>>>>

note: |
  May 15, 2023

authornote: | 
  This paper's open science repository: https://github.com/jianchenggu/MScThesis
  An earlier version of this article was submitted in partial fulfillment of the requirements for the degree -- Master of Science in Societal Resilience (Research).

@@

I adopted `R` (version 4.3.0) for all the analyses [@R-base]. This involved the following packages: `tidyverse` (version 2.0.0) and `haven` (version 2.5.2) for data cleaning [@R-tidyverse; @R-haven]; `fixest` (version 0.11.1) for econometric modeling [@R-fixest]; `MatchIt` (version 4.5.3) and `cobalt` (version 4.5.0) for matching [@ho2011; @R-MatchIt; @R-cobalt]; `modelsummary` (version 1.3.0), `vtable` (version 1.4.2), and `kableExtra` (version 1.3.4) for presenting the results [@R-modelsummary; @R-vtable; @R-kableExtra]; and `papaja` (version 0.1.1) for typesetting [@R-papaja].

@@

My research adds to the burgeoning evidence in favor of policy change on the hukou system. China's multilevel citizenship scheme powered by hukou shall not remain as it is, despite the small reduction of newly left-behind children's schooling performance. The slight drop is only the short-term consequence; The lifelong cumulative effect on children may be extensive [@liang2020; @meng2017]. Besides, educational attainment is only part of human development outcomes. Other outcomes like mental health and non-cognitive skills are also subjected to parental absence's influence [@antia2020; @pang2022].

Policymakers should accelerate the reforms on hukou, opening more doors for parents to migrate together with their children. In January 2023, local government officials lifted hukou restrictions in Zhengzhou, a city that hosts twelve million residents and the world's largest iPhone manufacturing plant [@jiemiannews2023; @deng2023]. This metropolis in central China set the precedant for offering hukou to all arriving migrants; Other main cities should follow suit. Besides top-down policymaking, bottom-up approaches are also necessary. School administrators could dedicate more advisory and counseling programs. Social workers could provide paraprofessional training in communities [@wang2020a].

### 2023-06-09 MScThesisText.tex
Update code, writing, bibliography

@@

An earlier version of this article was submitted in partial fulfillment of the requirements for the degree -- Master of Science in Societal Resilience (Research)

@@

I adopted \texttt{R} (version 4.2.2) for all the analyses (R Core Team, 2022). This involved the following packages: \texttt{tidyverse} (version 2.0.0) and \texttt{haven} (version 2.5.2) for data cleaning (Wickham et al., 2019, 2023); \texttt{fixest} (version 0.11.1) for econometric modeling (Berge et al., 2023); \texttt{MatchIt} (version 4.5.2) and \texttt{cobalt} (version 4.5.0) for matching (Greifer, 2023; Ho et al., 2023, 2011); \texttt{modelsummary} (version 1.3.0), \texttt{vtable} (version 1.4.2), and \texttt{kableExtra} (version 1.3.4) for presenting the results (Arel-Bundock, 2022; Huntington-Klein, 2023; Zhu, 2021); and \texttt{papaja} (version 0.1.1) for typesetting (Aust \& Barth, 2022).

@@

\caption{Parental migration’s effect on children’s cognitive test score, estimated with matching}
\centering
\begin{tabular}[t]{lcccc}
\toprule
  & Any Parent & Only Mother & Only Father & Both Parents\\
\midrule
Migration & \num{-2.53}** & \num{-2.82}* & \num{-2.78}* & \num{-1.72}\\
 & (\num{0.75}) & (\num{1.18}) & (\num{1.16}) & (\num{1.56})\\
Baseline.score & \num{-0.72}*** & \num{-0.72}*** & \num{-0.65}*** & \num{-0.74}***\\
 & (\num{0.03}) & (\num{0.03}) & (\num{0.04}) & (\num{0.05})\\
\midrule
Num.Obs. & \num{2540} & \num{1044} & \num{1024} & \num{523}\\
R2 & \num{0.402} & \num{0.454} & \num{0.405} & \num{0.493}\\
R2 Adj. & \num{0.375} & \num{0.391} & \num{0.338} & \num{0.382}\\
FE: schids & X & X & X & X\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
\multicolumn{5}{l}{\rule{0pt}{1em}3:1 optimal pair propensity score matching; exact matching by county}\\
\end{tabular}
\end{table}

@@

\caption{Parental migration’s effect on children’s academic exam score, estimated with matching}
\centering
\begin{tabular}[t]{lcccc}
\toprule
  & Any Parent & Only Mother & Only Father & Both Parents\\
\midrule
Migration & \num{-1.17}* & \num{-1.61}* & \num{-1.48} & \num{0.05}\\
 & (\num{0.57}) & (\num{0.76}) & (\num{0.89}) & (\num{0.93})\\
Baseline.score & \num{0.05} & \num{0.10}** & \num{0.06} & \num{0.02}\\
 & (\num{0.03}) & (\num{0.03}) & (\num{0.04}) & (\num{0.04})\\
\midrule
Num.Obs. & \num{2540} & \num{1044} & \num{1024} & \num{523}\\
R2 & \num{0.462} & \num{0.590} & \num{0.453} & \num{0.513}\\
R2 Adj. & \num{0.437} & \num{0.542} & \num{0.391} & \num{0.406}\\
FE: schids & X & X & X & X\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
\multicolumn{5}{l}{\rule{0pt}{1em}3:1 optimal pair propensity score matching; exact matching by county}\\
\end{tabular}
\end{table}

@@

My research adds to the burgeoning evidence in favor of policy change on the hukou system. China's multilevel citizenship scheme powered by hukou shall not remain as it is, despite the small reduction of newly left-behind children's schooling performance. The slight drop is only the short-term consequence; The lifelong cumulative effect on children may be extensive (Liang \& Sun, 2020; Meng \& Yamauchi, 2017). Besides, educational attainment is only part of human development outcomes. Other outcomes like mental health and non-cognitive skills are also subjected to parental absence's influence (Antia et al., 2020; Pang \& Lu, 2022). Policymakers should accelerate the reforms on hukou, opening more doors for parents to migrate together with their children. In January 2023, local government officials lifted hukou restrictions in Zhengzhou, a city that hosts twelve million residents and the world's largest iPhone manufacturing plant (Deng, 2023; Jiemian News, 2023). This metropolis in central China set the precedant for offering hukou to all arriving migrants. Other main cities should follow suit. Besides top-down policymaking, bottom-up approaches are also necessary. School administrators could dedicate more advisory and counseling programs. Social workers could provide paraprofessional training in communities (M. Wang et al., 2020).

@@

\caption{Parental migration’s effect on children’s cognitive test score, estimated with matching}
\centering
\begin{tabular}[t]{lcccc}
\toprule
  & Any Parent & Only Mother & Only Father & Both Parents\\
\midrule
Migration & \num{-2.43}** & \num{-3.18}** & \num{-3.18}* & \num{-1.80}\\
 & (\num{0.73}) & (\num{1.12}) & (\num{1.21}) & (\num{1.59})\\
Baseline.score & \num{-0.79}*** & \num{-0.80}*** & \num{-0.75}*** & \num{-0.83}***\\
 & (\num{0.03}) & (\num{0.04}) & (\num{0.04}) & (\num{0.05})\\
child.age & \num{-2.74}*** & \num{-2.07}* & \num{-3.25}** & \num{-3.93}***\\
 & (\num{0.59}) & (\num{0.92}) & (\num{0.99}) & (\num{1.08})\\
child.is.girl & \num{-1.12} & \num{0.56} & \num{-1.35} & \num{-2.19}\\
 & (\num{0.72}) & (\num{1.18}) & (\num{1.23}) & (\num{1.48})\\
child.health & \num{-0.20} & \num{0.56} & \num{-1.40}* & \num{-0.49}\\
 & (\num{0.41}) & (\num{0.58}) & (\num{0.65}) & (\num{0.90})\\
child.has.rural.hukou & \num{-0.42} & \num{-0.08} & \num{-1.49} & \num{-3.06}\\
 & (\num{0.87}) & (\num{1.28}) & (\num{1.32}) & (\num{2.18})\\
child.number.of.sibling & \num{-0.75} & \num{-1.15} & \num{-0.32} & \num{-0.08}\\
 & (\num{0.54}) & (\num{0.82}) & (\num{0.72}) & (\num{1.46})\\
child.went.to.preschool & \num{2.22}* & \num{1.49} & \num{2.93}* & \num{6.00}**\\
 & (\num{0.90}) & (\num{1.57}) & (\num{1.32}) & (\num{1.82})\\
child.had.skipped.grade & \num{-2.14} & \num{-0.51} & \num{-5.84} & \num{1.59}\\
 & (\num{2.92}) & (\num{3.94}) & (\num{4.78}) & (\num{5.92})\\
child.had.repeated.grade & \num{-1.04} & \num{-6.67}* & \num{-2.16} & \num{-0.45}\\
 & (\num{0.98}) & (\num{3.09}) & (\num{1.67}) & (\num{2.06})\\
child.in.boarding.school & \num{1.92} & \num{2.78} & \num{2.32} & \num{0.67}\\
 & (\num{1.35}) & (\num{2.58}) & (\num{2.06}) & (\num{2.31})\\
child.education.aspiration & \num{1.93}*** & \num{1.03} & \num{1.69}*** & \num{2.20}**\\
 & (\num{0.39}) & (\num{0.58}) & (\num{0.42}) & (\num{0.80})\\
child.is.ethnic.minority & \num{3.65}** & \num{-0.21} & \num{-0.82} & \num{2.90}\\
 & (\num{1.21}) & (\num{1.77}) & (\num{4.00}) & (\num{4.18})\\
parent.expectation & \num{2.11}*** & \num{3.46}*** & \num{2.56}*** & \num{1.92}*\\
 & (\num{0.46}) & (\num{0.89}) & (\num{0.59}) & (\num{0.91})\\
parent.has.white.collar.job & \num{1.49} & \num{1.69} & \num{1.25} & \num{0.98}\\
 & (\num{0.93}) & (\num{1.24}) & (\num{1.55}) & (\num{2.91})\\
mother.education.level & \num{0.03} & \num{-0.16} & \num{-0.08} & \num{0.29}\\
 & (\num{0.39}) & (\num{0.64}) & (\num{0.79}) & (\num{1.09})\\
father.education.level & \num{0.41} & \num{0.48} & \num{0.21} & \num{-1.12}\\
 & (\num{0.42}) & (\num{0.47}) & (\num{0.76}) & (\num{0.92})\\
home.economic.resource & \num{-0.88} & \num{-3.04}** & \num{-0.03} & \num{0.63}\\
 & (\num{0.73}) & (\num{1.13}) & (\num{1.20}) & (\num{1.44})\\
home.extracurricular.book & \num{-0.12} & \num{0.16} & \num{0.53} & \num{0.62}\\
 & (\num{0.38}) & (\num{0.55}) & (\num{0.51}) & (\num{0.69})\\
home.has.internet & \num{-0.96} & \num{-0.30} & \num{-1.34} & \num{-2.55}\\
 & (\num{0.70}) & (\num{1.91}) & (\num{1.31}) & (\num{2.37})\\
\midrule
Num.Obs. & \num{2540} & \num{1044} & \num{1024} & \num{523}\\
R2 & \num{0.448} & \num{0.502} & \num{0.473} & \num{0.566}\\
R2 Adj. & \num{0.418} & \num{0.434} & \num{0.402} & \num{0.448}\\
FE: schids & X & X & X & X\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
\multicolumn{5}{l}{\rule{0pt}{1em}3:1 optimal pair propensity score matching; exact matching by county}\\
\end{tabular}
\end{table}

@@

\caption{Parental migration’s effect on children’s academic exam score, estimated with matching}
\centering
\begin{tabular}[t]{lcccc}
\toprule
  & Any Parent & Only Mother & Only Father & Both Parents\\
\midrule
Migration & \num{-1.18}* & \num{-2.02}** & \num{-1.61} & \num{-0.35}\\
 & (\num{0.55}) & (\num{0.76}) & (\num{0.88}) & (\num{1.02})\\
Baseline.score & \num{0.06}* & \num{0.04} & \num{-0.02} & \num{-0.03}\\
 & (\num{0.03}) & (\num{0.04}) & (\num{0.04}) & (\num{0.05})\\
child.age & \num{-0.20} & \num{-0.33} & \num{-0.44} & \num{-0.60}\\
 & (\num{0.29}) & (\num{0.45}) & (\num{0.47}) & (\num{0.54})\\
child.is.girl & \num{1.83}*** & \num{1.90}*** & \num{1.99}** & \num{1.14}\\
 & (\num{0.47}) & (\num{0.52}) & (\num{0.63}) & (\num{1.21})\\
child.health & \num{0.68}** & \num{1.18}*** & \num{0.55} & \num{0.89}\\
 & (\num{0.21}) & (\num{0.33}) & (\num{0.31}) & (\num{0.52})\\
child.has.rural.hukou & \num{0.08} & \num{0.75} & \num{-0.10} & \num{0.95}\\
 & (\num{0.50}) & (\num{0.75}) & (\num{0.71}) & (\num{1.09})\\
child.number.of.sibling & \num{0.17} & \num{-0.09} & \num{0.26} & \num{0.59}\\
 & (\num{0.26}) & (\num{0.32}) & (\num{0.43}) & (\num{0.65})\\
child.went.to.preschool & \num{1.11} & \num{1.78}* & \num{0.05} & \num{2.59}*\\
 & (\num{0.67}) & (\num{0.84}) & (\num{0.86}) & (\num{1.21})\\
child.had.skipped.grade & \num{0.23} & \num{-2.73} & \num{0.15} & \num{7.91}\\
 & (\num{2.71}) & (\num{2.36}) & (\num{2.91}) & (\num{4.33})\\
child.had.repeated.grade & \num{-0.62} & \num{-2.74} & \num{-1.49} & \num{0.75}\\
 & (\num{0.81}) & (\num{1.54}) & (\num{1.07}) & (\num{1.11})\\
child.in.boarding.school & \num{0.02} & \num{1.63} & \num{0.05} & \num{-0.98}\\
 & (\num{0.70}) & (\num{1.01}) & (\num{0.90}) & (\num{1.58})\\
child.education.aspiration & \num{0.49}* & \num{0.85}** & \num{0.91}** & \num{-0.13}\\
 & (\num{0.23}) & (\num{0.26}) & (\num{0.30}) & (\num{0.53})\\
child.is.ethnic.minority & \num{0.36} & \num{-0.31} & \num{0.54} & \num{-2.08}\\
 & (\num{0.86}) & (\num{0.88}) & (\num{1.42}) & (\num{1.93})\\
parent.expectation & \num{0.60}** & \num{0.15} & \num{0.62} & \num{1.01}\\
 & (\num{0.22}) & (\num{0.45}) & (\num{0.33}) & (\num{0.62})\\
parent.has.white.collar.job & \num{0.65} & \num{0.10} & \num{1.08} & \num{-0.39}\\
 & (\num{0.44}) & (\num{0.59}) & (\num{0.80}) & (\num{1.42})\\
mother.education.level & \num{-0.20} & \num{0.12} & \num{-0.16} & \num{-0.20}\\
 & (\num{0.26}) & (\num{0.28}) & (\num{0.32}) & (\num{0.58})\\
father.education.level & \num{0.25} & \num{0.10} & \num{0.02} & \num{0.28}\\
 & (\num{0.20}) & (\num{0.30}) & (\num{0.32}) & (\num{0.52})\\
home.economic.resource & \num{-0.05} & \num{0.18} & \num{-0.14} & \num{-1.00}\\
 & (\num{0.38}) & (\num{0.52}) & (\num{0.55}) & (\num{0.62})\\
home.extracurricular.book & \num{-0.33} & \num{-0.59}* & \num{-0.25} & \num{0.52}\\
 & (\num{0.22}) & (\num{0.30}) & (\num{0.30}) & (\num{0.40})\\
home.has.internet & \num{-0.92}* & \num{-0.95} & \num{-0.64} & \num{0.79}\\
 & (\num{0.42}) & (\num{0.73}) & (\num{0.59}) & (\num{1.09})\\
\midrule
Num.Obs. & \num{2540} & \num{1044} & \num{1024} & \num{523}\\
R2 & \num{0.489} & \num{0.616} & \num{0.482} & \num{0.545}\\
R2 Adj. & \num{0.461} & \num{0.563} & \num{0.412} & \num{0.420}\\
FE: schids & X & X & X & X\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
\multicolumn{5}{l}{\rule{0pt}{1em}3:1 optimal pair propensity score matching; exact matching by county}\\
\end{tabular}
\end{table}

>>>>

\authornote{

This paper's open science repository: \url{https://github.com/jianchenggu/MScThesis}
An earlier version of this article was submitted in partial fulfillment of the requirements for the degree -- Master of Science in Societal Resilience (Research).

@@

May 15, 2023

@@

I adopted \texttt{R} (version 4.3.0) for all the analyses (R Core Team, 2022). This involved the following packages: \texttt{tidyverse} (version 2.0.0) and \texttt{haven} (version 2.5.2) for data cleaning (Wickham et al., 2019, 2023); \texttt{fixest} (version 0.11.1) for econometric modeling (Berge et al., 2023); \texttt{MatchIt} (version 4.5.3) and \texttt{cobalt} (version 4.5.0) for matching (Greifer, 2023; Ho et al., 2023, 2011); \texttt{modelsummary} (version 1.3.0), \texttt{vtable} (version 1.4.2), and \texttt{kableExtra} (version 1.3.4) for presenting the results (Arel-Bundock, 2022; Huntington-Klein, 2023; Zhu, 2021); and \texttt{papaja} (version 0.1.1) for typesetting (Aust \& Barth, 2022).

@@

\caption{Parental migration’s effect on children’s cognitive test score, estimated with matching}
\centering
\begin{tabular}[t]{lcccc}
\toprule
  & Any Parent & Only Mother & Only Father & Both Parents\\
\midrule
Migration & \num{-2.54}*** & \num{-2.55}* & \num{-2.65}* & \num{-0.34}\\
 & (\num{0.75}) & (\num{1.14}) & (\num{1.10}) & (\num{1.54})\\
Baseline.score & \num{-0.70}*** & \num{-0.70}*** & \num{-0.65}*** & \num{-0.71}***\\
 & (\num{0.03}) & (\num{0.04}) & (\num{0.04}) & (\num{0.05})\\
\midrule
Num.Obs. & \num{2540} & \num{1044} & \num{1024} & \num{523}\\
R2 & \num{0.396} & \num{0.445} & \num{0.410} & \num{0.486}\\
R2 Adj. & \num{0.368} & \num{0.380} & \num{0.343} & \num{0.372}\\
FE: schids & X & X & X & X\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
\multicolumn{5}{l}{\rule{0pt}{1em}3:1 optimal pair propensity score matching; exact matching by county}\\
\end{tabular}
\end{table}

@@

\caption{Parental migration’s effect on children’s academic exam score, estimated with matching}
\centering
\begin{tabular}[t]{lcccc}
\toprule
  & Any Parent & Only Mother & Only Father & Both Parents\\
\midrule
Migration & \num{-1.15}* & \num{-1.72}* & \num{-1.53} & \num{0.50}\\
 & (\num{0.56}) & (\num{0.75}) & (\num{0.81}) & (\num{0.84})\\
Baseline.score & \num{0.05} & \num{0.08}* & \num{0.04} & \num{0.03}\\
 & (\num{0.03}) & (\num{0.04}) & (\num{0.04}) & (\num{0.04})\\
\midrule
Num.Obs. & \num{2540} & \num{1044} & \num{1024} & \num{523}\\
R2 & \num{0.456} & \num{0.574} & \num{0.436} & \num{0.522}\\
R2 Adj. & \num{0.431} & \num{0.524} & \num{0.373} & \num{0.415}\\
FE: schids & X & X & X & X\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
\multicolumn{5}{l}{\rule{0pt}{1em}3:1 optimal pair propensity score matching; exact matching by county}\\
\end{tabular}
\end{table}

@@

My research adds to the burgeoning evidence in favor of policy change on the hukou system. China's multilevel citizenship scheme powered by hukou shall not remain as it is, despite the small reduction of newly left-behind children's schooling performance. The slight drop is only the short-term consequence; The lifelong cumulative effect on children may be extensive (Liang \& Sun, 2020; Meng \& Yamauchi, 2017). Besides, educational attainment is only part of human development outcomes. Other outcomes like mental health and non-cognitive skills are also subjected to parental absence's influence (Antia et al., 2020; Pang \& Lu, 2022).

Policymakers should accelerate the reforms on hukou, opening more doors for parents to migrate together with their children. In January 2023, local government officials lifted hukou restrictions in Zhengzhou, a city that hosts twelve million residents and the world's largest iPhone manufacturing plant (Deng, 2023; Jiemian News, 2023). This metropolis in central China set the precedant for offering hukou to all arriving migrants; Other main cities should follow suit. Besides top-down policymaking, bottom-up approaches are also necessary. School administrators could dedicate more advisory and counseling programs. Social workers could provide paraprofessional training in communities (M. Wang et al., 2020).

@@

\caption{Parental migration’s effect on children’s cognitive test score, estimated with matching}
\centering
\begin{tabular}[t]{lcccc}
\toprule
  & Any Parent & Only Mother & Only Father & Both Parents\\
\midrule
Migration & \num{-2.51}*** & \num{-2.44}* & \num{-3.02}* & \num{-0.32}\\
 & (\num{0.72}) & (\num{1.10}) & (\num{1.18}) & (\num{1.63})\\
Baseline.score & \num{-0.78}*** & \num{-0.77}*** & \num{-0.74}*** & \num{-0.79}***\\
 & (\num{0.03}) & (\num{0.04}) & (\num{0.04}) & (\num{0.05})\\
child.age & \num{-2.77}*** & \num{-1.37} & \num{-3.19}** & \num{-3.23}*\\
 & (\num{0.58}) & (\num{1.02}) & (\num{0.96}) & (\num{1.30})\\
child.is.girl & \num{-1.73}* & \num{0.40} & \num{-1.44} & \num{-1.21}\\
 & (\num{0.67}) & (\num{1.16}) & (\num{1.22}) & (\num{1.67})\\
child.health & \num{-0.26} & \num{0.90} & \num{-1.22} & \num{-0.93}\\
 & (\num{0.41}) & (\num{0.66}) & (\num{0.62}) & (\num{0.96})\\
child.has.rural.hukou & \num{-0.33} & \num{-0.61} & \num{-1.68} & \num{-2.70}\\
 & (\num{0.84}) & (\num{1.22}) & (\num{1.24}) & (\num{2.16})\\
child.number.of.sibling & \num{-0.76} & \num{-1.32} & \num{-0.52} & \num{0.41}\\
 & (\num{0.55}) & (\num{0.83}) & (\num{0.75}) & (\num{1.31})\\
child.went.to.preschool & \num{1.97}* & \num{1.33} & \num{2.76}* & \num{6.17}***\\
 & (\num{0.88}) & (\num{1.43}) & (\num{1.30}) & (\num{1.74})\\
child.had.skipped.grade & \num{-1.81} & \num{-1.39} & \num{-7.72}* & \num{2.21}\\
 & (\num{2.98}) & (\num{4.34}) & (\num{3.86}) & (\num{4.77})\\
child.had.repeated.grade & \num{-1.02} & \num{-5.79}* & \num{-2.10} & \num{-1.29}\\
 & (\num{1.02}) & (\num{2.69}) & (\num{1.78}) & (\num{2.08})\\
child.in.boarding.school & \num{1.60} & \num{1.74} & \num{1.70} & \num{-0.47}\\
 & (\num{1.30}) & (\num{1.85}) & (\num{2.08}) & (\num{2.50})\\
child.education.aspiration & \num{1.97}*** & \num{0.84} & \num{1.48}*** & \num{2.08}*\\
 & (\num{0.38}) & (\num{0.61}) & (\num{0.41}) & (\num{0.88})\\
child.is.ethnic.minority & \num{3.12}* & \num{-2.31} & \num{0.02} & \num{3.82}\\
 & (\num{1.34}) & (\num{2.56}) & (\num{4.54}) & (\num{4.98})\\
parent.expectation & \num{2.19}*** & \num{3.56}*** & \num{2.36}*** & \num{2.11}*\\
 & (\num{0.46}) & (\num{0.77}) & (\num{0.54}) & (\num{0.96})\\
parent.has.white.collar.job & \num{0.84} & \num{0.14} & \num{0.13} & \num{0.94}\\
 & (\num{0.95}) & (\num{1.28}) & (\num{1.41}) & (\num{2.98})\\
mother.education.level & \num{0.26} & \num{-0.02} & \num{0.31} & \num{0.43}\\
 & (\num{0.38}) & (\num{0.70}) & (\num{0.81}) & (\num{1.03})\\
father.education.level & \num{0.66} & \num{0.78} & \num{0.41} & \num{-0.29}\\
 & (\num{0.40}) & (\num{0.49}) & (\num{0.74}) & (\num{1.05})\\
home.economic.resource & \num{-0.61} & \num{-2.22} & \num{0.00} & \num{0.72}\\
 & (\num{0.70}) & (\num{1.31}) & (\num{1.11}) & (\num{1.55})\\
home.extracurricular.book & \num{-0.15} & \num{0.43} & \num{0.58} & \num{1.31}\\
 & (\num{0.38}) & (\num{0.57}) & (\num{0.50}) & (\num{0.74})\\
home.has.internet & \num{-1.34} & \num{0.14} & \num{-1.52} & \num{-3.90}*\\
 & (\num{0.72}) & (\num{1.87}) & (\num{1.20}) & (\num{1.94})\\
\midrule
Num.Obs. & \num{2540} & \num{1044} & \num{1024} & \num{523}\\
R2 & \num{0.445} & \num{0.490} & \num{0.469} & \num{0.554}\\
R2 Adj. & \num{0.415} & \num{0.419} & \num{0.397} & \num{0.431}\\
FE: schids & X & X & X & X\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
\multicolumn{5}{l}{\rule{0pt}{1em}3:1 optimal pair propensity score matching; exact matching by county}\\
\end{tabular}
\end{table}

@@

\caption{Parental migration’s effect on children’s academic exam score, estimated with matching}
\centering
\begin{tabular}[t]{lcccc}
\toprule
  & Any Parent & Only Mother & Only Father & Both Parents\\
\midrule
Migration & \num{-1.18}* & \num{-1.89}* & \num{-1.52} & \num{0.20}\\
 & (\num{0.55}) & (\num{0.73}) & (\num{0.81}) & (\num{0.87})\\
Baseline.score & \num{0.06}* & \num{0.02} & \num{-0.04} & \num{-0.01}\\
 & (\num{0.03}) & (\num{0.04}) & (\num{0.04}) & (\num{0.04})\\
child.age & \num{-0.15} & \num{-0.13} & \num{-0.67} & \num{-1.00}*\\
 & (\num{0.30}) & (\num{0.45}) & (\num{0.48}) & (\num{0.48})\\
child.is.girl & \num{1.74}*** & \num{1.61}** & \num{2.45}*** & \num{0.49}\\
 & (\num{0.47}) & (\num{0.54}) & (\num{0.64}) & (\num{1.06})\\
child.health & \num{0.60}** & \num{1.19}** & \num{0.51} & \num{0.65}\\
 & (\num{0.21}) & (\num{0.36}) & (\num{0.29}) & (\num{0.52})\\
child.has.rural.hukou & \num{-0.11} & \num{0.63} & \num{-0.13} & \num{0.84}\\
 & (\num{0.50}) & (\num{0.73}) & (\num{0.69}) & (\num{1.02})\\
child.number.of.sibling & \num{0.08} & \num{0.14} & \num{0.54} & \num{0.27}\\
 & (\num{0.25}) & (\num{0.30}) & (\num{0.37}) & (\num{0.65})\\
child.went.to.preschool & \num{1.34}* & \num{2.36}* & \num{0.02} & \num{2.57}*\\
 & (\num{0.65}) & (\num{0.98}) & (\num{0.77}) & (\num{1.11})\\
child.had.skipped.grade & \num{-0.13} & \num{-2.17} & \num{0.28} & \num{6.06}\\
 & (\num{2.74}) & (\num{2.63}) & (\num{2.84}) & (\num{4.65})\\
child.had.repeated.grade & \num{-0.19} & \num{-0.64} & \num{-1.02} & \num{0.19}\\
 & (\num{0.85}) & (\num{1.52}) & (\num{1.06}) & (\num{1.09})\\
child.in.boarding.school & \num{-0.28} & \num{-0.92} & \num{0.98} & \num{0.01}\\
 & (\num{0.72}) & (\num{1.54}) & (\num{0.90}) & (\num{1.63})\\
child.education.aspiration & \num{0.44} & \num{1.18}** & \num{0.78}* & \num{0.01}\\
 & (\num{0.23}) & (\num{0.38}) & (\num{0.30}) & (\num{0.50})\\
child.is.ethnic.minority & \num{0.23} & \num{-1.07} & \num{-0.35} & \num{-3.44}\\
 & (\num{0.88}) & (\num{0.98}) & (\num{1.82}) & (\num{2.15})\\
parent.expectation & \num{0.67}** & \num{0.02} & \num{0.98}* & \num{0.55}\\
 & (\num{0.22}) & (\num{0.44}) & (\num{0.40}) & (\num{0.57})\\
parent.has.white.collar.job & \num{0.37} & \num{-0.10} & \num{1.75}* & \num{-0.18}\\
 & (\num{0.41}) & (\num{0.60}) & (\num{0.79}) & (\num{1.28})\\
mother.education.level & \num{-0.08} & \num{-0.06} & \num{-0.15} & \num{-0.03}\\
 & (\num{0.26}) & (\num{0.31}) & (\num{0.34}) & (\num{0.53})\\
father.education.level & \num{0.25} & \num{0.24} & \num{-0.06} & \num{-0.01}\\
 & (\num{0.21}) & (\num{0.33}) & (\num{0.32}) & (\num{0.46})\\
home.economic.resource & \num{0.03} & \num{0.21} & \num{-0.24} & \num{-1.04}\\
 & (\num{0.37}) & (\num{0.60}) & (\num{0.54}) & (\num{0.69})\\
home.extracurricular.book & \num{-0.37} & \num{-0.67}* & \num{-0.08} & \num{0.33}\\
 & (\num{0.22}) & (\num{0.27}) & (\num{0.31}) & (\num{0.36})\\
home.has.internet & \num{-1.03}* & \num{-0.50} & \num{-0.55} & \num{0.25}\\
 & (\num{0.43}) & (\num{0.71}) & (\num{0.68}) & (\num{1.11})\\
\midrule
Num.Obs. & \num{2540} & \num{1044} & \num{1024} & \num{523}\\
R2 & \num{0.482} & \num{0.601} & \num{0.473} & \num{0.544}\\
R2 Adj. & \num{0.454} & \num{0.545} & \num{0.402} & \num{0.419}\\
FE: schids & X & X & X & X\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
\multicolumn{5}{l}{\rule{0pt}{1em}3:1 optimal pair propensity score matching; exact matching by county}\\
\end{tabular}
\end{table}
